Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-06-08 manuscript/manuscript.Rmd
Update manuscript.Rmd

```{r load_data}
# loads the processed data files output by the preprocessing performed above
load(here('data', 'processed', 'data_valuesLevel.RData')) # load data
load(here('data', 'processed', 'data_articlesLevel.RData')) # load data
load(here('data', 'processed', 'data_kidwell.RData')) # load data
```

>>>>

```{r load_data}
# loads the processed data files output by the preprocessing performed above
load(here('data', 'processed', 'data_values.RData')) # load data
load(here('data', 'processed', 'data_articles.RData')) # load data
load(here('data', 'processed', 'data_kidwell.RData')) # load data
```
